\subsection{Minimum requirements for provenance information}\label{sec:requirements}

This document was developed with those general requirements in mind:

\begin{itemize}

% == other models / serialisation

\item Provenance information must be formalized following a standard model, with corresponding standard serialization formats.

\item Provenance information must be machine readable.

\item Provenance data model classes and attributes should be linked, when relevant, to IVOA semantics, data models and formats (ObsCoreDM, SimDM, VOTable, UCDs, Units, \ldots).

\item Provenance information should be serializable into the W3C provenance standard formats (PROV-N, PROV-XML, PROV-JSON) with minimum information loss.

\end{itemize}

The following additional requirements are recommended when managing provenance information within the VO context:

\begin{itemize}

% == links between entity/activity

\item Provenance information must be endorsed by an authority (the person, organization or project providing this information).

\item Provenance metadata for a given entity must contain information to find immediate progenitor(s) up to an initial entity.
%All produced entities must contain information to find its immediate progenitor(s).

\item An entity must be linked to the activity that generated it up to an initial entity.
%Provenance metadata must contain information to find the activity that generated a given entity.
%* All produced entities must contain information to find the activity that generated it

\item Activities must be linked to input entities up to an initial activity.
%(if applicable).

\item Activities should point to output entities.

\item Provenance information should make it possible to derive the logical sequence of activities.
%The order of the activities should be available.

%\item Provenance information should contain the list of activities and progenitor entities.
% too vague .... must be an ordered list ... One step should also be allowed.

\item Entities, Activities and Agents must be uniquely identifiable within a domain.
% Provenance information can only be given for uniquely identifiable entities, at least inside their domain.

\item Released entities should have a main contact.

\item All activities and entities should have contact information and contain a (short) description or link to a description.
% could also be the documentation.

\end{itemize}

